State of the Art Review on Privacy-Preserving Signatures, Credentials, and Authentication

### 2021-11-15 prism-backend/research/soa_review/ac.tex
Added note on CGM16 (primitives for ACs with generic policies.)

@@

@@

\begin{itemize}
\item \cite{bcc+09,cklm14}: Delegation (\cite{cklm14} relies on \cite{cklm12}).
\item \cite{cgm16} An AC system that builds ACs from existing (conventional,
  such as ECDSA) signatures.
\end{itemize}

>>>>

\paragraph{Primitives for credentials with generic policies.} \cite{cgm16}
describes techniques to be able to create efficient proofs that combine both
algebraic and non-algebraic relations. For instance, proving knowledge of an
ECDSA or RSA-FDH signature (both of which include computation of a hash
function); but also being able to prove any arbitrary (non-algebraic) funcion
$f$. This may be very useful to achieve compatibility with traditional
credentials/signature schemes, that mostly do not follow the algorithms
used in anonymous credentials systems. In fact, that is one of the main
motivations in the paper. The approach in \cite{cgm16} builds on committing
Oblivious Transfer and Garbled Circuits (not necessarily with privacy).
A closely related work seems to be \cite{dfkp16},
which achieves the same goal but using SNARKS, which results in different
tradeoffs -- hence, it may be interesting, as the SNARK domain has improved
significantly since 2016. \cite{kkl+16} also allows building anonymous
credentials for arbitrary policies, but using a different approach too.

@@

Also:

\begin{itemize}
  \item ACs based on aggregate signatures: \cite{cl11}.
\end{itemize}

@@

\begin{itemize}
\item \cite{bcc+09,cklm14}: Delegation (\cite{cklm14} relies on \cite{cklm12}).
\item \cite{cgm16} An AC system that builds ACs from existing (conventional,
  such as ECDSA) signatures. \cite{kkl+16} achieves similar results with a
  different approach?
\end{itemize}
